---
output:
  html_document: default
  pdf_document: default
---
The first step is to load and preprocess the data. For instance,

```{r exploreData}
# Boxplot analysis

boxplot(male_students$IMC, female_students$IMC, main="BMI Analysis", col=(c("gold","darkgreen")),
        ylab="BMI Value")


legend("topright", inset=.02, title="Gender",
       c("Male","Female"), fill=(c("gold","darkgreen")), horiz=TRUE, cex=0.8)
```

To get an initial feel for the relationships between the relevant variables of your experiment it is frequently interesting to perform some preliminary (exploratory) analysis. This is frequently referred to as _getting a feel_ of your data, and can suggest procedures (such as outlier investigation or data transformations) to experienced experimenters.

```{r exploreData}
hgA <- hist(male_students$IMC, breaks = 12)
hgB <- hist(female_students$IMC)

plot(hgA, col ='gold', xlim = c(13,40), xlab = 'BMI', main ='BMI Histogram')
plot(hgB, add = TRUE, col = 'darkgreen')

legend("topright", inset=.02, title="Gender",
       c("Male","Female"), fill=(c("gold","darkgreen")), horiz=TRUE, cex=0.75)
```
Your preliminary analysis should be described together with the plots. In this example, two facts are immediately clear from the plots: first, **mpg** tends to correlate well with many of the other variables, most intensely with **drat** (positively) and **wt** (negatively). It is also clear that many of the variables are highly correlated (e.g., **wt** and **disp**). Second, it seems like manual transmission models present larger values of **mpg** than the automatic ones. In the next section a linear model will be fit to the data in order to investigate the significance and magnitude of this possible effect.