To check if the chosen model is correct and the assumptions in the testing phase were evaluated correctly, the data's normality is tested

### Second Experiment
The second experiment tests if there's a difference in the BMI of male students from different semesters. 

#### Independence of samples:
aaa


#### Normality check:

For verifying distribution normality, the Shapiro-Wilk test is applied. If the p-value is less than our significance level of 0.05, then the null hypothesis is rejected, and the data is not normally distributed.

```{r test2_norm_check}

p_male_stundents2016 <-shapiro.test(male_students2016$IMC)$p.value #OK
p_male_stundents2017 <-shapiro.test(male_students2017$IMC)$p.value #OK

```

The results above indicates:

- 2016/2 students p-value = `r p_male_stundents2016`  
- 2017/2 students p-value = `r p_male_stundents2017`  

Since the p-value is greater than 0.05, the null hypothesis is not rejected, and the data is normally distributed. A plot demonstrating data normality can be seen below.


```{r test2_norm_checkplot}

par(mfrow=c(1,2))
qqPlot(male_students2016$IMC, main="2016/2 male students")
qqPlot(male_students2017$IMC, main="2017/2 male students")

```


#### Independence of samples:
aaa

- Data: Male and Female



```{r}
p_female_stundents <- shapiro.test(female_students$IMC)$p.value #OK
qqPlot(female_students$IMC)

p_male_stundents <- shapiro.test(male_students$IMC)$p.value #OK
qqPlot(male_students$IMC)

```



- Data: Female 2016-2 and Female 2017-2
```{r}
p_female_stundents2016 <-shapiro.test(female_students2016$IMC)$p.value #OK
qqPlot(female_students2016$IMC)
p_female_stundents2017 <-shapiro.test(female_students2017$IMC)$p.value #NOT OK
qqPlot(female_students2017$IMC)
```

Since the dataset 'female_students2017' cannot be assumed normal, a non-parametric test must be issued for this case:

```{r}
wilcox.test(female_students2016$IMC,female_students2017$IMC)
```